How to obtain the redshift distribution from probabilistic redshift estimates

### 2017-06-28 research/paper/draft.tex
periodic update

It is useful to translate some popular existing methods for deriving $n(z)$ 
from photo-$z$ PDFs into the mathematical framework of Sec. \ref{sec:model}.  
We do not advocate for these methods for reasons addressed in the Appendix.

@@

The most common way to combine photo-$z$ PDFs into an estimator 
$\hat{n}_{stack}(z)$ for $n(z)$ is to stack them, which corresponds to
\begin{align}
\label{eq:stack}
\hat{n}^{stack}(z) &= \frac{1}{N}\ \sum_{i}^{N} p(z_{i} | \vec{d}_{i}, 
\vec{\phi}^{*}).
\end{align}

@@

In some cases, estimators $\hat{n}(z)$ are obtained by assuming the photo-$z$ 
PDFs are effectively delta functions by reducing them to point estimates 
according to
\begin{align}
\label{eq:delta}
p(z_{i} | \vec{d}_{i}, \vec{\phi}^{*}) &\approx \delta(z, \hat{z}_{i}^{point})
\end{align}
before applying Eq. \ref{eq:stack}.  The most common redshift point estimators 
are the mean $\hat{z}^{mean}_{i}$, median $\hat{z}^{median}_{i}$, and mode 
$\hat{z}^{mode}_{i}$ of the original photo-$z$ interim posterior.

>>>>

It is useful to translate some popular existing methods for deriving $n(z)$ 
from photo-$z$ PDFs into the mathematical framework of Sec. \ref{sec:model}.  
We briefly discuss the conditions under which they are equivalent to Eq. 
\ref{eq:final}, which are elaborated upon in the Appendix.

@@

The most common way to combine photo-$z$ interim posteriors into an estimator 
$\hat{n}_{stack}(z)$ for $n(z)$ is to "stack" them, which corresponds to
\begin{align}
\label{eq:stack}
\hat{n}^{stack}(z) &= \frac{1}{N}\ \sum_{i}^{N} \exp\left[\log[p(z_{i} | 
\vec{d}_{i}, \vec{\phi}^{*})]\right].
\end{align}

@@

In some cases, estimators $\hat{n}^{point}(z)$ are obtained by assuming the 
photo-$z$ PDFs are effectively delta functions by reducing them to point 
estimates according to
\begin{align}
\label{eq:delta}
p(z_{i} | \vec{d}_{i}, \vec{\phi}^{*}) &\approx \delta(z, \hat{z}_{i}^{point})
\end{align}
before applying Eq. \ref{eq:stack}.  The most popular redshift point estimators 
are the mean $\hat{z}^{mean}_{i}$, median $\hat{z}^{median}_{i}$, and mode 
$\hat{z}^{mode}_{i}$ of the original photo-$z$ interim posterior.
